### 2022-05-15 manuscript.Rmd
Make sure random seed gets used for all models

# Re-run steps that take a long time?
run <- list(
  bayesian_models = FALSE,
  jackknife_analysis = FALSE,
  sensitivity_analysis = FALSE
)

@@

# Run Bayesian multilevel model
res_meta <- update(
  res_prior_meta,
  sample_prior = FALSE,
  file = here(models_dir, "res_meta"),
  file_refit = brms_file_refit
)
summary(res_meta)

@@

# Run Bayesian multilevel model
res_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  file = here(models_dir, "res_reg"),
  file_refit = brms_file_refit
)
summary(res_reg)

@@

# Run Bayesian multilevel model
res_gender <- update(
  res_prior_gender,
  sample_prior = FALSE,
  file = here(models_dir, "res_gender"),
  file_refit = brms_file_refit
)
summary(res_gender)

>>>>

# Re-run steps that take a long time?
run <- list(
  bayesian_models = TRUE,
  jackknife_analysis = FALSE,
  sensitivity_analysis = FALSE
)

@@

# Run Bayesian multilevel model
res_meta <- update(
  res_prior_meta,
  sample_prior = FALSE,
  seed = seed,
  file = here(models_dir, "res_meta"),
  file_refit = brms_file_refit
)
summary(res_meta)

@@

# Run Bayesian multilevel model
res_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  seed = seed,
  file = here(models_dir, "res_reg"),
  file_refit = brms_file_refit
)
summary(res_reg)

@@

# Run Bayesian multilevel model
res_gender <- update(
  res_prior_gender,
  sample_prior = FALSE,
  seed = seed,
  file = here(models_dir, "res_gender"),
  file_refit = brms_file_refit
)
summary(res_gender)

### 2022-05-15 supplement.Rmd
Make sure random seed gets used for all models

  # Re-fit the meta-analysis, leaving out one experiment at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
    dat_jackknife <- dat_meta[-jackknife_index, ]
    res_jackknife <- update(res_meta, newdata = dat_jackknife, refresh = 0)
    print_res_table(
      res_jackknife,
      label_1 = dat_meta$article[jackknife_index],
      label_2 = dat_meta$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) %>%
    # Show article labels only for the first experiment (row) per article
    mutate(
      Article = if_else(Article == lag(Article, default = ""), "", Article),
    ) -> tabs3

@@

      # Re-run meta-analysis of mental rotation performance
      res_meta <- update(res_meta, newdata = dat_ri_sens, refresh = 0)

      # Re-run meta-regression of mental rotation performance
      res_reg <- update(res_reg, newdata = dat_ri_sens, refresh = 0)

@@

      # Re-run meta-analysis of mental rotation performance
      res_meta <- update(res_meta, prior = prior_sens, refresh = 0)

      # Re-run meta-regression of mental rotation performance
      res_reg <- update(res_reg, prior = prior_sens, refresh = 0)

      # Re-run meta-analysis of gender differences
      res_gender <- update(res_gender, prior = prior_sens, refresh = 0)

>>>>

  # Re-fit the meta-analysis, leaving out one experiment at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat_meta)), function(jackknife_index) {
    dat_jackknife <- dat_meta[-jackknife_index, ]
    res_jackknife <- update(
      res_meta,
      newdata = dat_jackknife,
      seed = seed,
      refresh = 0
    )
    print_res_table(
      res_jackknife,
      label_1 = dat_meta$article[jackknife_index],
      label_2 = dat_meta$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) %>%
    # Show article labels only for the first experiment (row) per article
    mutate(
      Article = if_else(Article == lag(Article, default = ""), "", Article),
    ) -> tabs3

@@

      # Re-run meta-analysis of mental rotation performance
      res_meta <- update(
        res_meta,
        newdata = dat_ri_sens,
        seed = seed,
        refresh = 0
      )

      # Re-run meta-regression of mental rotation performance
      res_reg <- update(
        res_reg,
        newdata = dat_ri_sens,
        seed = seed,
        refresh = 0
      )

@@

      # Re-run meta-analysis of mental rotation performance
      res_meta <- update(
        res_meta,
        prior = prior_sens,
        seed = seed,
        refresh = 0
      )

      # Re-run meta-regression of mental rotation performance
      res_reg <- update(
        res_reg,
        prior = prior_sens,
        seed = seed,
        refresh = 0
      )

      # Re-run meta-analysis of gender differences
      res_gender <- update(
        res_gender,
        prior = prior_sens,
        seed = seed,
        refresh = 0
      )
